Finite Property Convex Elicitation Paper

### 2019-01-28 cvx-fin.tex
Added statements in the Appendix

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
  \item $\trim(\Gamma)$ is a finite set.
  \item There is a finite set of maximal level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
  \end{enumerate}
  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$.
\end{proposition}
\begin{proof}
  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
  (Note that the second equality follows from the definition of embedding.)
  Clearly, $\trim(\Gamma) \supseteq \{\gamma_r : r \in \R\}$ as we are simply restricting the number of level sets we are indexing over.
  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
  If $u \in \varphi(\R)$, then clearly we are done.
  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since the level sets composing $\trim$ are unlabeled.
  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
  If $\Gamma_u$ is maximal, it must be unique up to relabeling\jessiet{skimmed over this, but follows from the convexity of the scoring rule... it's in detail in my writeup.  My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}, giving us one of the first two cases or a contradiction of elicitability.
  If $\Gamma_u$ is not maximal, it must be a subset of some maximal level set\jessiet{also in my notes... going to suggest the same footnote/appendix proof- like the other note.}, and therefore not in $\trim(\Gamma)$.
  Thus, we conclude $\trim(\Gamma) \subseteq \{\gamma_r : r \in \R\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.

@@

\begin{definition}
  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ \jessiet{$d \geq 1?$}\raft{Technically constant properties $\gamma(p) = \{c\} \forall p$ would have complexity 0.  Not terribly interesting... but it would also feel weird to call that complexity $1$.  Hmm.} such that $\gamma$ is $d$-embeddable.
\end{definition}

@@

\subsection*{For Proposition 9}
\begin{lemma}\label{lem:trim-full-dim}
  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
\end{lemma}
\begin{proof}
  \jessiet{TODO}
\end{proof}

\begin{lemma}
Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not maximal.
\end{lemma}
\begin{proof}
  \jessiet{TODO}
\end{proof}

>>>>

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
  \item $\trim(\Gamma)$ is a finite set.
  \item There is a finite set of maximal level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
  \end{enumerate}
  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$.
\end{proposition}
\begin{proof}
  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
  (Note that the second equality follows from the definition of embedding.)
  Clearly, $\trim(\Gamma) \supseteq \{\gamma_r : r \in \R\}$ as we are simply restricting the number of level sets we are indexing over.
  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
  If $u \in \varphi(\R)$, then clearly we are done.
  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since the level sets composing $\trim$ are unlabeled.
  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
  If $\Gamma_u$ is maximal, it must be unique up to relabeling (see Lemma~\ref{lem:trim-subsets-not-maximal} in the Appendix)\jessiet{skimmed over this, but follows from the convexity of the scoring rule.  My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}, giving us one of the first two cases or a contradiction of elicitability.
  If $\Gamma_u$ is not maximal, it must be a subset of some maximal level set\jessiet{also in my notes... going to suggest the same footnote/appendix proof- like the other note.}, and therefore not in $\trim(\Gamma)$.
  Thus, we conclude $\trim(\Gamma) \subseteq \{\gamma_r : r \in \R\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.

@@

\begin{definition}
  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\geq 0$ such that $\gamma$ is $d$-embeddable.
\end{definition}

@@

\section{Considering unlabeled properties}
\begin{lemma}\label{lem:trim-full-dim}
  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
  Every $\theta \in \Theta := \trim(\Gamma)$ is maximal.  
\end{lemma}
\begin{proof}
  Consider an arbitrary level set $\theta$.
  If $\theta$ is not maximal, then it must be the intersection of some maximal level sets in $\trim(\Gamma)$.
  Therefore, it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
\end{proof}

\begin{lemma}\label{lem:trim-subsets-not-maximal}
Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not maximal.
\end{lemma}
\begin{proof}
  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
  There is a set $\D \subseteq \partial_p G$, and we note that there is a bijection $\phi:\D \to \R$ so that the subgradients of $G$ correspond to the property value at the distribution $p$.

  If there is a maximal level set $\Gamma_u$ that is a proper subset of $\Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for every distribution $p \in \Gamma_u$.
  However, closed, convex, maximal level sets have positive Lebesgue measure in $\reals^n$, and thus $G$ can not be differentiable on $\Gamma_u$.
  This contradicts the convexity of $G$, as convex functions are differentiable almost everywhere, which in turn contradicts the elicitability of $\Gamma$.
  Therefore, we conclude that $\Gamma_u$ is not maximal.
\end{proof}
